\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{titling}
\usepackage{hyperref}
\usepackage[hyphens]{url}
\usepackage[normalem]{ulem}

\geometry{a4paper, margin=1in}

\title{JPL - Moon Augmented Reality \\ Design Specification}
\author{Group 2}
\date{December 2025}

\setlength{\droptitle}{6cm}

\pagestyle{fancy}
\fancyhead[L]{JPL - Moon Augmented Reality Design Spec}
\fancyhead[C]{}
\fancyhead[R]{Page \thepage}

\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}

\thispagestyle{empty}
\tableofcontents
\newpage

This Design Specification provides a concise breakdown of all major parts, modules, tools, and components used in the MoonTrek: Telescope Augmented Reality project.  
It expands the Software Design Document (SDD) by describing each system part in slightly more detail.

% ----------------------------------------------------------
\section{System Parts and Modules}

\subsection{User Interface Module (UIM)}

\subsubsection*{Purpose}
The UIM displays the web application's visual interface, handles user interactions, and forwards user inputs (such as uploaded images and metadata) to the backend.

\subsubsection*{Components / Tools Used}
\begin{itemize}
    \item HomePage.vue
    \item UploadPage.vue
    \item ModelPage.vue
    \item ConnectPage.vue
    \item Supporting components: AnimatedStars.vue, ImageCanvas.vue, ImageUploadForm.vue, NavBar.vue
\end{itemize}

\subsubsection*{Inputs and Outputs}
\begin{itemize}
    \item \textbf{Inputs:} user-uploaded images, metadata, navigation actions
    \item \textbf{Outputs:} overlays, 3D model display, telescope connection interface
\end{itemize}


\subsection{Registration Module (RM)}

\subsubsection*{Purpose}
The RM processes and registers the user’s Moon image by comparing it with a reference image to generate a transformation matrix.

\subsubsection*{Components / Tools Used}
\begin{itemize}
    \item SIFT feature detection
    \item Circle detection algorithm
    \item Transformation matrix computation
\end{itemize}

\subsubsection*{Inputs and Outputs}
\begin{itemize}
    \item \textbf{Inputs:} cropped user image, reference Moon image
    \item \textbf{Outputs:} transformation matrix for overlay placement
\end{itemize}


\subsection{3D Model Module (3DM)}

\subsubsection*{Purpose}
The 3DM generates a photorealistic 3D model of the Moon, Earth, and Sun based on the user's location and image timestamp.

\subsubsection*{Components / Tools Used}
\begin{itemize}
    \item Three.js rendering engine
    \item NASA lunar texture maps and reference datasets
\end{itemize}

\subsubsection*{Inputs and Outputs}
\begin{itemize}
    \item \textbf{Inputs:} latitude, longitude, date, time metadata
    \item \textbf{Outputs:} rendered Moon reference image for registration
\end{itemize}


% ----------------------------------------------------------
\section{Directory Structure}

As described in the SDD, the project consists of a \texttt{client} and \texttt{server} directory.

\subsection{Client Directory}
Contains all UI-related Vue components, styling, and route definitions.

\subsection{Server Directory}
Contains:
\begin{itemize}
    \item \texttt{process.py} – Runs RM algorithms.
    \item Reference images used during image registration.
    \item Express.js endpoint handlers for uploads and metadata.
\end{itemize}

% ----------------------------------------------------------
\section{Tools and Technologies}

This section provides a concise breakdown of every tool used, aligning with the SDD.

\subsection{Vue.js}
Used for UI structure, routing, and page components.

\subsection{Express.js}
Provides backend routing and communication logic between modules.

\subsection{Python (process.py)}
Executes SIFT and related image-processing procedures.

\subsection{MySQL}
Stores user-uploaded images and associated metadata.

\subsection{JavaScript Cropping Utility}
Allows users to crop Moon images before processing.

\subsection{Three.js}
Renders the 3D model of the Moon, Earth, and Sun.

\subsection{NASA MoonTrek API}
Supplies scientific lunar data used for annotations and overlays.

% ----------------------------------------------------------
\section{User Interface Summary}

The application implicitly consists of:

\begin{itemize}
    \item Home Screen
    \item Upload Screen
    \item 3D Model Screen
    \item Telescope Connection Screen
\end{itemize}

Each corresponds directly to a Vue component already listed under the UIM section.  
No additional UI details are necessary for this Design Spec.

\end{document}